Comparative analysis of PMV Models accuracy implemented in the ISO 7730:2005 and ASHRAE 55:2023

### 2024-10-30 Manuscript/src/sections/appendix.tex
feat(code): analysis three height and t threshold

The overall bias of the \ac{pmv} and \ac{pmv-ce} models is shown in Figure~\ref{fig:hist_discrepancies_three_heights}.
\begin{figure}[htb!]
    \centering
    \includegraphics[width=\textwidth]{figures/hist_discrepancies_three_heights}
    \caption{Bias of the \ac{pmv} and \ac{pmv-ce} models for the dataset with air speed measured at three heights.}
    \label{fig:hist_discrepancies_three_heights}
\end{figure}
The \ac{pmv} model has a bias of \num{-.28} while the \ac{pmv-ce} model has a bias of \num{-.38}.
The interquartile range for the \ac{pmv} model is more centered around \num{0} than the \ac{pmv-ce} model.
These results allow us to conclude that the \ac{pmv} model is more accurate than the \ac{pmv-ce} model for the dataset with air speed measured at three heights.

>>>>

The overall bias of the \ac{pmv} and \ac{pmv-ce} models is shown in Figure~\ref{fig:hist_discrepancies_three_heights}.
\begin{figure}[htb!]
    \centering
    \includegraphics[width=\textwidth]{figures/hist_discrepancies_three_heights}
    \caption{Bias of the \ac{pmv} and \ac{pmv-ce} models for the dataset with air speed measured at three heights.}
    \label{fig:hist_discrepancies_three_heights}
\end{figure}
The \ac{pmv} model has a bias of \num{-.28} while the \ac{pmv-ce} model has a bias of \num{-.39}.
The interquartile range for the \ac{pmv} model is more centered around \num{0} than the \ac{pmv-ce} model.
These results allow us to conclude that the \ac{pmv} model is more accurate than the \ac{pmv-ce} model for the dataset with air speed measured at three heights.

\subsection{Dataset with \ac{v} measured at three heights and \ac{tdb}~$\geq$~\qty{24}{\celsius}}\label{subsec:dataset-with-v-measured-at-three-heights-and-tdb-geq-24-celsius}
Here we are showing the results for the subset of data with \ac{v} measured at three heights and \ac{tdb}~$\geq$~\qty{24}{\celsius}.
We are also reporting these results since the \ac{pmv-ce} aims to more accurately predict the thermal sensation, compared to the \ac{pmv}, when air movement is used to cool the occupants.
The results are shown in Figure~\ref{fig:hist_discrepancies_three_heights_limit_t}.
\begin{figure*}[htb!]
    \centering
    \includegraphics[width=\textwidth]{figures/hist_discrepancies_three_heights_limit_t}
    \caption{Bias of the \ac{pmv} and \ac{pmv-ce} models for the dataset with air speed measured at three heights and \ac{tdb}~$\geq$~\qty{24}{\celsius}.}
    \label{fig:hist_discrepancies_three_heights_limit_t}
\end{figure*}
Even for this subset of data, the \ac{pmv} model is more accurate than the \ac{pmv-ce} model.
The \ac{pmv} model has a bias of \num{-.08} while the \ac{pmv-ce} model has a bias of \num{-.31}.
This result is consistent with the previous analysis and confirms that the \ac{pmv} model is more accurate than the \ac{pmv-ce}.
